### 2016-07-08 filters-notions.tex
no message

@@

\jnote{How do we want to define a ``secure'' Bloom filter (even
informally)? Do we want to say that the probability of finding a
false positive is negligible? Or that if we set the FP rate to
$\epsilon$ then the best an attacker can do with $q$ hash queries is
$1-(1-\epsilon)^q$ plus negligible?} 
\tsnote{Formally, I don't think we can (and still be rooted in
  reality.)  Even informally it's hard, since the fact is that the
  designer decides what is ``secure'' for her setting.  I think we
  just say something like ``A bloom filter is
  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
you like, we can throw a paramter~$n$ in there, for the number of FPs
it must find.)  Perhaps informally we say that a bloom filter is
secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
not ``significantly larger'' than the designer's target.  I guess
that's not far off from one of your suggestions.}

@@

\jnote{What parameters are needed to get negligible $\epsilon$? Are
they reasonable in practice?} \tsnote{Again, I don't think that
negligible is reasonable in practice :P}

>>>>

\jnote{Do our definitions imply the Naor definition? If so, then why do they use a PRP
in their construction?}

@@

\jnote{How do we want to define a ``secure'' Bloom filter (even
informally)? Do we want to say that the probability of finding a
false positive is negligible? Or that if we set the FP rate to
$\epsilon$ then the best an attacker can do with $q$ hash queries is
$1-(1-\epsilon)^q$ plus negligible?}
\tsnote{Formally, I don't think we can (and still be rooted in
  reality).  Even informally it's hard, since the fact is that the
  designer decides what is ``secure'' for her setting.  I think we
  just say something like ``A bloom filter is
  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
you like, we can throw a paramter~$n$ in there, for the number of FPs
it must find.)  Perhaps informally we say that a bloom filter is
secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
not ``significantly larger'' than the designer's target.  I guess
that's not far off from one of your suggestions.}

@@

### 2016-07-08 intro.tex
no message

Syntactically, NY says a Bloom filter (with a steady representation)
is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a
set~$\mathcal{S}$ it returns a representation~$M$ (from some
undefined, implicit set of representations).  The query
algorithm~$\mathcal{B}_2$ is deterministic, and on input a
representation~$M$ and an element~$x \in \mathcal{U}$, it returns a
bit.  For correctness they make the classical demand, that for all
$x \in \mathcal{S}$ we have
$\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For
soundness, adversary~$A$ plays the following game,
``Adversarial-resilient Bloom Filter with a steady representation''.
First, $M \getsr \mathbf{B}_1(\mathcal{S})$. \jnote{Where does the
set come from? Is it random? Adversarially chosen?}
\tsnote{In their formalism, it is implicitly an input to the security experiment.
Security is universally quantified over sets~$\mathcal{S}$.  This
would seem to be equivalent to letting the adversary
pick~$\mathcal{S}$ (prior to the hash functions being picked), with
the time to compute and write out~$\mathcal{S}$ folded into the
adversary's running time. } 
Then the
adversary is given the set~$\mathcal{S}$ and may make queries
$x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At
the end of its execution, the adversary outputs~$x^*$ and wins the
game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$,
and (2) $\mathbf{B}_2(M,x^*)=1$.

@@

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; 
\jnote{I think this is also reasonable; typically
security is defined without regard for efficiency}
\tsnote{My complaint isn't about efficiency. It's about the fact that,
by not including $|M|$ in the definition, the trivial scheme I give
(just below) is allowed, and is secure.  Anyway, as I say at the end
of this paragraph, this is a small(er) complaint than what follows}. The surrounding
text does say that $\mathbf{B}_1$ ``outputs a compressed
representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
but what exactly this means is never addressed.  The formal syntax
admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints.  But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

@@

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can be used for set membership.  Builds a secret-key data structure (an Index) that allows searching for keyword~$w$ if one holds the trapdoor $T_w$ for~$w$, where the trapdoor depends on the secret key.  Main construction uses traditional Bloom filters and a PRF.  Construction appears quite inefficient, needing a very long secret key, turning a keyword~$w$ into a bunch of PRF outputs, and then storing each of these PRF outputs in the BF.  Havent read the full analysis; don't know if this was ever published. }
\end{itemize}

>>>>

Syntactically, NY says a Bloom filter (with a steady representation)
is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a
set~$\mathcal{S}$ it returns a representation~$M$ (from some
undefined, implicit set of representations).  The query
algorithm~$\mathcal{B}_2$ is deterministic, and on input a
representation~$M$ and an element~$x \in \mathcal{U}$, it returns a
bit.  For correctness they make the classical demand, that for all
$x \in \mathcal{S}$ we have
$\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For
soundness, adversary~$A$ plays the following game,
``Adversarial-resilient Bloom Filter with a steady representation''.
First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set
$\mathcal{S}$ that can be adversarially chosen. Then the adversary
may make queries $x_1,x_2,\ldots,x_q$ to an oracle for
$\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary
outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup
\{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.

@@

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!} The
surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed
representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
but what exactly this means is never addressed.  The formal syntax
admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints.  But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

@@

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Havent read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}
